Distinction Centrality Analysis

### 2025-07-18 analysis.qmd
new updated

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

```{r}
   make.broker.graphs <- function(n = 10) {
      g <- make_empty_graph(9, directed = FALSE)
      g <- g + edge(1,2)
      g <- g + edge(1,3)
      g <- g + edge(2,4)
      g <- g + edge(2,5)
      g <- g + edge(2,6)
      g <- g + edge(3,7)
      g <- g + edge(3,8)
      g <- g + edge(3,9)
      el <- vector(mode = "list", length = n)
      el[[1]] <- g
      a <- 10
      b <- 11
      c <- 12
      d <- 13
      for (i in 2:n) {
         g <- add_vertices(g, 4)
         g <- g + edge(1,a)
         g <- g + edge(a,b)
         g <- g + edge(a,c)
         g <- g + edge(a,d)
         el[[i]] <- g
         a <- a + 4
         b <- b + 4
         c <- c + 4
         d <- d + 4
      }
   return(el)
   }
   b <- make.broker.graphs(30)
   c <- lapply(b, distinction.new, norm = FALSE)
```

@@

```{r}
   d.s <- sapply(c, function(x) {x[1, 3]})
   d.b <- sapply(c, function(x) {x[2, 3]})
   dat <- data.frame(d = c(d.s, d.b), 
         n = c(1:length(d.s)+1, 1:length(d.s)+1),
         g = c(rep(1, length(d.s)), rep(2, length(d.s))))
   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
   p <- p + geom_point(size = 3)
   p <- p + geom_line(linewidth = 0.75)
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   #p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"),
                  legend.title = element_blank(),
                  legend.position = "none"
                  )
   p <- p + ggtitle("Scalar Distinction of Star versus Gatekeeper Node")
   p
   ggsave(here("Plots", "star-v-gate-by-nbranches.png"), width = 7, height = 7, units = "in")
```

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "distinction.new.R"))
   source(here("Functions", "make.broker.trees.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

```{r}

   b <- make.broker.graphs(30)
   c <- lapply(b, distinction.new, norm = FALSE)
```

@@

```{r}
   d.s <- sapply(c, function(x) {x[1, 3]})
   d.b <- sapply(c, function(x) {x[2, 3]})
   d.p <- sapply(c, function(x) {x[nrow(x), 3]})
   dat <- data.frame(d = c(d.s, d.b, d.p), 
         n = c(1:length(d.s)+1, 1:length(d.s)+1, 1:length(d.s)+1),
         g = c(rep(1, length(d.s)), rep(2, length(d.s)), 
         rep(3, length(d.s))))
   p <- ggplot(dat, aes(n, d, group = g, color = as.factor(g))) 
   p <- p + geom_point(size = 3)
   p <- p + geom_line(linewidth = 0.75)
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "", x = "Number of Branches")
   p <- p + scale_x_continuous(breaks = seq(2, length(d), by = 2))
   #p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"),
                  legend.title = element_blank(),
                  legend.position = "none"
                  )
   p <- p + ggtitle("Scalar Distinction of Star versus Gatekeeper Node")
   p
   ggsave(here("Plots", "star-v-gate-by-nbranches.png"), width = 7, height = 7, units = "in")
```
